A holomorphic approach to branes in twisted~$M$-theory

### 2022-09-21 fivebranes/index.tex
ss

Before proceeding with the construction, let us first give some feel for the situation we hope to describe. Suppose we consider a gravitational theory on $AdS_{d+1}\times S^{d^{\prime}}$, which we compactify to view as a theory on $AdS_{d+1}$ with all Kaluza-Klein harmonics included. Let $M^{d}$ denote the conformal boundary of $AdS_{d+1}$. A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{}. Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

@@

We wish to describe $\cA^{\bu}_{F}$-modules, for $F$ an involutive subbundle appearing in the top row of the above diagram. To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the directions in which the leaves lie. Explicitly, let $\cA_{\mathring M/\R_{>0}\times Z} = \cA_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}}$, $F_{\R_{>0}\times Z} = T_{\R_{>0}}\oplus T^{0,1}_{Z}$ and $\cA_{\R_{>0}\times Z} = \cA_{\pi^{*} F _{\R_{>0}\times Z}}$. Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.

The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
\[
  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}\otimes \cL
\]

@@

In \cite{KormanThesis}, the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ is interpreted as defining a superconnection on the pushforward $\pi_{*}\cA^{\bu}_{\mathring M/R_{>0}\times Z}$ viewed as the sheaf of sections of a complex of pro-vector bundles on $\R_{+}\times Z$.

\surya{finish}

@@

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^{\bu}_{F_{\R_{>0}\times Z}}\left(H^\bu(\cA^\bu_{F_{\mathring M/ R_{>0}\times Z}}(\cL), \thfd)\right)
  \eeqn

  The BV pairing is given by
  \beqn
  \int_{}
  \eeqn

@@

The model for the pushforward in the previous proposition appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KormanThesis} that converges to the cohomology with respect to the totalized differential $D+\thfd$ $H^{\bullet}(\cA_{\mathring M}(\cL), D+\thfd)$. In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where $M = Tot (\R\oplus \C^{2}\to \C^{3})$. We recall the result. Fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.

\surya{sloppy about hypercohomology}
\begin{prop}
  Up to completion, the cohomology $H^{\bu}(\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd)$ is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA)(L), \thfd)$ with the complex

>>>>

Before proceeding with the construction, let us first give some feel for the situation we hope to describe. Suppose we consider a gravitational theory on $AdS_{d+1}\times S^{d^{\prime}}$, which we compactify to view as a theory on $AdS_{d+1}$ with all Kaluza-Klein harmonics included. Let $M^{d}$ denote the conformal boundary of $AdS_{d+1}$. A supergravity state is traditionally defined to be a solution to linearized equations of motion with a given boundary value \cite{WittenHolography}. Typically, this definition is made in situations where the relevant boundary value problem has a unique solution, in which case one may label states by the corresponding boundary values. Moreover, one may think of such boundary values as arising from modifications of a vacuum boundary condition at a point.

@@

For each of the involutive subbundles $F$ appearing in the top row of the above diagram, we wish to describe certain  To make the burden less cumbersome, we will drop mention of the foliation and instead refer to the whether the leaves lie along the base or fiber of the submersion $p$.

Explicitly, we set
\begin{align*}
  \cA^{\bu}_{\mathring M/\R_{>0}\times Z} & = \cA^{\bu}_{F_{\mathring M}\cap T^{\C}_{\mathring M/ \R_{>0}\times Z}} \\
  F_{\R_{>0}\times Z} &  = T_{\R_{>0}}\oplus T^{0,1}_{Z} \text{ so }p^{*}F_{\R_{>0}\times Z} = h^{*}T_{\R_{>0}}\oplus \pi^{*}T^{0,1}_{Z} \\
  \cA^{\bu}_{\R_{>0}\times Z}&  = \cA^{\bu}_{F _{\R_{>0}\times Z}} \text{ so }p^{*}\cA^{\bu}_{\R_{>0}\times Z} = \cA^{\bu}_{p^{*}F _{\R_{>0}\times Z}}
\end{align*}

Our goal is to describe the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ as a $\cA^{\bu}_{\R_{>0}\times Z}$-module.

The splitting affords an isomorphism of $C^{\infty}_{\mathring M}$-modules
\[
  \cA^{\bu}_{\mathring M}(L)\cong \cA^{\bu}_{\R_{>0}\times Z}\otimes \cA^{\bu}_{{\mathring M/ \R_{>0}\times Z}}(L)
\]

@@

We now analyze the THF differential $\thfD$ on $\cA^{\bu}_{\mathring M}(L)$ under the above splitting.
\surya{finish}

@@

\begin{prop}
  The pushforward $(p| \mathring M)_{*}\cL_{sugra}$ is described by the following complex of sheaves
  \beqn
  \cA^\bu_{\R_{>0}\times Z}\otimes \mathbb{R}^\bu p_* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L) \right)
  \eeqn

  The BV pairing is given by
  \beqn
  \eeqn

@@

The previous result gives a description of the compactification of $\cL_{sugra}$ on the link of fivebranes as a free holomorphic-topological BV theory on $\R_{>0}\times Z$. In particular, the result is local on $R_{>0}\times Z$. For computing the space of states, it will be useful to have a description of its global sections. For the computation of numerical invariants such as graded characters, of the space of states, a more drastic simplification is useful. Indeed, we may anticipate cohomological cancellations in the character and instead compute the character of any cochain complex that a spectral sequence whose first page is the global sections abuts to.

The global sections of the sheaf in proposition \ref{dimred} appears naturally on the $E_{1}$-page of a Leray-Serre-type spectral sequence \cite{KamberTondeur}
\beqn
E_1^{p,q} = \Gamma \left (\R_{>0}\times Z; \cA^p_{\R_{>0}\times Z}\otimes \mathbb{R}^q p _* \left (\cA^\bu_{\mathring M / \R_{>0}\times Z}(L)\right) \right)\implies \mathbb{H}^{p+q} (\cA^\bu_{\mathring M}(L)).
\eeqn
We emphasize that no page of this spectral sequence involves cohomology with respect to the operators $D, D_{\Omega}$; these differentials are kept internal.

In \cite{RSW}, this spectral sequence was implicitly used to give a concrete description of the pushforward $(p|\mathring M)_{*}\cL_{sugra}$ in the case where
\beqn
M = Tot (\R\oplus \C^{2}\to \C^{3}), \ \ \ \ \ \ \mathring M = \R\times \C^2\times \C^3 \setminus (0 \times \C^3).
\eeqn

To recall the result, fix holomorphic coordinates $z_{i}, i=1, 2, 3$ on $\C^{3}$ and holomorphic fiber coordinates $w_{a}, a= 1, 2$ on $\C^{2}$.

\begin{prop}
  Up to completion, the cohomology
  \beqn
  \mathbb H^{\bu} (\cA_{\mathring M}^\bu (L) ) = H^{\bu}\left (\Gamma(\cA_{\mathring M}^{\bu}(L)), \thfd\right)
  \eeqn
  is a direct sum of the cohomology on flat space $H^{\bu}(\Gamma(\cA_{M}^{\bu}(L), \thfd)$ with the complex
